Does Phase Delay Dramatically Increase Cost to Fix?

### 2015-07-28 phaseDelay.tex
files reorged into 'old' and 'img'

%timm tricks
\newcommand{\bi}{\begin{itemize}[leftmargin=0.4cm]}
\newcommand{\ei}{\end{itemize}}
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}
\newcommand{\tion}[1]{\S\ref{sect:#1}}
\newcommand{\fig}[1]{Figure~\ref{fig:#1}}
\newcommand{\eq}[1]{Equation~\ref{eq:#1}}

\usepackage[shortlabels]{enumitem} 
\usepackage{times}

@@

\setlist{nosep}

\usepackage{colortbl}
 \usepackage[font={small}]{caption, subfig}
\setlength{\abovecaptionskip}{1ex}
 \setlength{\belowcaptionskip}{1ex}
 \setlength{\floatsep}{1ex}
 \setlength{\textfloatsep}{1ex}
\usepackage[compact,small]{titlesec}
\DeclareMathSizes{7}{7}{7}{7} 
\pagenumbering{arabic}
\setlength{\columnsep}{7mm}

@@

\conferenceinfo{FSE}{'15 Bergamo, Italy}
\title{Revisiting the Truisms of Software Engineering:\\ Does Phase Delay Dramatically Increase  Fix Time?}
\numberofauthors{5}
\author{
\alignauthor 
Tim Menzies \\
       \affaddr{Dept. of Computer Science}\\
       \affaddr{North Carolina State U, USA}\\
       \email{tim.menzies@gmail.com}
\alignauthor 
William Nichols \\
        \affaddr{Software Engineering Institute}\\
        \affaddr{Carnegie Mellon U, USA}
        \email{wrn@sei.cmu.edu} 
\alignauthor 
Lucas Layman \\
       \affaddr{Fraunhofer CESE} \\
       \affaddr{College Park, USA}\\ 
       \email{llayman@fc-md.umd.edu}
\and
\alignauthor 
Forrest Shull \\
        \affaddr{Software Engineering Institute}\\
        \affaddr{Carnegie Mellon U, USA}
        \email{fjshull@sei.cmu.edu} 
\alignauthor 
Carter Pape \\
       \affaddr{Dept. of Computer Science}\\
       \affaddr{North Carolina State U, USA}\\
       \email{carterpape@gmail.com}
} 
\maketitle
\begin{abstract}
Does
repair time increase dramatically
the longer an issue persists in a system?
Many industrial practitioners and academics this   to be true.
This   belief is used to justify 
major investments in  software development
 processes and methods.

@@

\vspace{1mm}
\noindent
{\bf Keywords:} software processes, economics, phase delay, time to fix.

@@

\begin{figure}
 \includegraphics[width=3.3in]{beckB4.png}
 \caption{Projects exhibiting phase delay. From~\cite{beck00}.}\label{fig:curve1}
 \end{figure}
\begin{figure}
 \includegraphics[width=3.3in]{beckAFTER.png}
 \caption{Projects without   phase delay. From~\cite{beck00}.}\label{fig:curve2}
\end{figure}

@@

%\hspace{-0.7cm}
\begin{center}
\includegraphics[height=2in]{fix-phase-dist.pdf}
\end{center}
%~\\

@@

\begin{figure}[!t] 
%\vspace{-1cm}
%\hspace{-0.35in}
\begin{center}
\includegraphics[width=3in]{boehm-overlay.pdf}
 \end{center}
% ~\\~\\
%~\\~\\~\\

>>>>

%timm tricks
\newcommand{\bi}{\begin{itemize}}%[leftmargin=0.4cm]}
\newcommand{\ei}{\end{itemize}}
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}
\newcommand{\tion}[1]{\S\ref{sect:#1}}
\newcommand{\fig}[1]{Figure~\ref{fig:#1}}
\newcommand{\eq}[1]{Equation~\ref{eq:#1}}

\usepackage[shortlabels]{enumitem} 
%\usepackage{times}

@@

%\setlist{nosep}

\usepackage{colortbl}
 %\usepackage[font={small}]{caption, subfig}
%\setlength{\abovecaptionskip}{1ex}
 %\setlength{\belowcaptionskip}{1ex}
% \setlength{\floatsep}{1ex}
% \setlength{\textfloatsep}{1ex}
%\usepackage[compact,small]{titlesec}
\DeclareMathSizes{7}{7}{7}{7} 
\pagenumbering{arabic}
%\setlength{\columnsep}{7mm}

@@

\conferenceinfo{ICSE}{'16 Austin, Texas}
\title{Does Phase Delay Dramatically Increase Cost to Fix?}
\numberofauthors{3}
\author{
%\alignauthor 
Tim Menzies \\
       \affaddr{Dept. of Computer Science}\\
       \affaddr{North Carolina State U, USA}\\
       \email{tim.menzies@gmail.com}
\and%alignauthor 
William Nichols,Forest Shull \\
        \affaddr{Software Engineering Institute}\\
        \affaddr{Carnegie Mellon U, USA}\\
        \email{\{wrn,fjshull\}@sei.cmu.edu} 
\and %\alignauthor 
Lucas Layman \\
       \affaddr{Fraunhofer CESE} \\
       \affaddr{College Park, USA}\\ 
       \email{llayman@fc-md.umd.edu}
} 
\maketitle
\begin{abstract}
Does
repair time increase dramatically
the longer an issue persists in a system?
Many industrial practitioners and academics this   to be true.
This   belief is used to justify 
major investments in  software development
 processes and methods.

@@

\vspace{1mm}
\noindent
{\bf Keywords:} software processes, economics, phase delay, cost to fix.

@@

\begin{figure}
 \includegraphics[width=3.3in]{img/beckB4.png}
 \caption{Projects exhibiting phase delay. From~\cite{beck00}.}\label{fig:curve1}
 \end{figure}
\begin{figure}
 \includegraphics[width=3.3in]{img/beckAFTER.png}
 \caption{Projects without   phase delay. From~\cite{beck00}.}\label{fig:curve2}
\end{figure}

@@

%\hspace{-0.7cm}
\begin{center}
\includegraphics[height=2in]{img/fix-phase-dist.pdf}
\end{center}
%~\\

@@

\begin{figure}[!t] 
%\vspace{-1cm}
%\hspace{-0.35in}
\begin{center}
\includegraphics[width=3in]{img/boehm-overlay.pdf}
 \end{center}
% ~\\~\\
%~\\~\\~\\
